Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375

### 2015-02-28 papers/B1555_EdgeOn/B1555_letter.tex
Added new text from Simona

@@

A common feature of simulations of structure formation is the presence
of thousands of subhaloes that are associated with larger mass haloes.
However, observations of the Local Group find many fewer satellite
galaxies than are predicted by the simulations, even when taking into
account completeness corrections arising from the limited sky coverage
imposed by the Galactic Plane.  This is the famous ``missing
satellite'' problem \citep{Klypin1999, Moore1999, S07}.  In order to understand
this discrepancy, it is imperative to build up a large sample of satellites /
subhalos in galaxies outside the Local Group.  This process is challenging
due to the faintness of the satellite galaxies.  Furthermore, lower-mass
satellites may not be able to retain the gas needed for ongoing star
formation \citep[e.g.,][]{P11}, rendering them effectively dark.
These
factors make gravitational effects be powerful and promising tools in
the substructure searching.

	Flux ratio anomalies are seen in strong lensing systems which have multiple images that are spacially close to each other. These ``merging doubles'' share the same surface brightness in principle but happend to have different surface brightness. Little perturbation in gravitational potential is sufficent to bring flux ratio anomalies in strong lensed systems. This makes flux ratio anomaly becomes a promising tool to detect dark matter substructures \citep{Dalal2002, N13}. In radio band, lensing images are not sensitive to micro lensing from stars, and one can also avoid severe dust extinction issue like in optical or infrared band. However, only small number of flux ratio anomalous systems in radio are avaliable for analysis. Besides waiting for future large-scale survey such as LSST to find thousands of more new lens galaxies, another approach using narrow-line quasar emission \citep{N14} is capable to seek out more flux ratio anomalous systems for substructure analysis.

	With expected growth in the number of samples, several groups have developed the technique to estimate the properties of substructures from flux ratio anomalous systems. \citet{V09, H13} both analyze the strong lens imaging to detect substructures lie infront of Einstein ring. Their methods improve the detectable mass limit and also show that high spatial resolution imaging is essential for the substructure study. On the other hand, numerical simulations on structure formation do not reach the concise conclusion on flux ratio anomalous systems. The latest study on the cause of flux anomalies from \citet{Xu14} shows the low probability of the existence of substructures in their studied systems.

	The Strong lensing at High Angular Resolution Program(SHARP) is a project aims on known quadruple and Einstein ring lensing systems \citep{SHARP12}. We obtain high-resoltion images from Keck adaptive optics(AO) and Hubble Space Telescope(HST) observations. To better understand the cause of flux ratio anomaly in strong lensing systems, we model B1555+375, one of the systems discussed in \citet{Xu14}, with the new information obtained from the latest SHARP infrared imaging. We present the latest SHARP data in part 2, lens model of B1555+375 in part 3, and discussion in part 4.

@@

\begin{figure}
\plotone{B1555_Kp.eps}
\plottwo{B1555_model.eps}{B1555_residue.eps}
\caption{Left: SHARP K-band image of B1555+375 Middle: Lens model image generated by glafic Right: Residue image of B1555+375.\\
An edge-on disk can be seen in the center of SHARP K-band image. Exponential disk is marked by the green ellipse in residue image. We believe strong dust extinction from the edge-on disk makes B and D no detection in infrared. Thus leaving two negative holes in our residue.\label{fig1}}
\end{figure}

\begin{figure}
\plotone{point_source.eps}
\caption{Radio observation(red open circle) and model-predicted(blue plus sign) image positions of B1555+375. The position of the source is at $(-0.2066,-0.1634)$ for SIE+Expdisk model, marked by a black filled circle. From left to right, four components are A, B (merging doubles), D(lowest spot), and C(right).\label{fig2}}
\end{figure}

@@

\section{Discussion}
The abundance of substructure within galaxy-size halo has been an undetermined problem in structure formation studies. The discrepency between numerical simulations and observations within local universe gives two possible arguments: an alternative structure formation model or the selection bias of local universe samples. Lensing shows a promising potential on substructure detection beyond the Local Group. The main reason is that gravitational perturbation from the substructure reflects the total mass, regardless it's luminous or not.

>>>>

\usepackage{color}
\definecolor{simonacolor}{cmyk}{0, 0.9808, 0.4429, 0.1412}
\newcommand{\simona}[1]{\textcolor{simonacolor}{#1}}

@@

A common feature of simulations of structure formation is the presence
of thousands of subhaloes that are associated with larger mass haloes.
However, observations of the Local Group find many fewer satellite
galaxies than are predicted by the simulations, even when taking into
account completeness corrections arising from the limited sky coverage
imposed by the Galactic Plane.  This is the famous ``missing
satellite'' problem \citep{Klypin1999, Moore1999, S07}. In order to understand
this discrepancy, it is imperative to build up a large sample of satellites/\simona{subhaloes} in galaxies outside the Local Group.  
This process is challenging
due to the faintness of the satellite galaxies.  Furthermore, lower-mass
satellites may not be able to retain the gas needed for ongoing star
formation \citep[e.g.,][]{P11}, rendering them effectively dark.
These factors make gravitational \simona{lensing a powerful and promising tool for the detection of substructure.}

\simona{It was first suggested by Mao \& Schneider 1998 that flux ratio anomalies observed in radio loud multiple images of lensed quasar could be interpreted as the telltale of the presence of substructure in lens galaxies.}
%Flux ratio anomalies are seen in strong lensing systems which have multiple images that are spacially close to each other. These ``merging doubles'' share the same surface brightness in principle but happend to have different surface brightness. 
\simona{Indeed,} little perturbation\simona{s} in \simona{the} gravitational potential \simona{are} sufficent to bring flux ratio anomalies in strong lensed systems. 
\simona{Moreover, unlike in the optical or infrared,} in \simona{the} radio band, lens\simona{ed} images are not sensitive to micro lensing from stars \simona{nor dust extinction}. 
This makes flux ratio anomalies a promising tool to detect dark matter substructures \citep{Dalal2002, N13}.  
\simona{At present, the amount of substructure derived from flux ratio anomalies is in disagreement with predictions from numerical simulations, with the former requiring a larger fraction of mass in substructure than expected \citet{Xu14}. While this could be the result of small sample statistics, it could also be the indication that flux ratio anomalies have a different origin than substructure.} \simona{An alternative method for the detection of substructure in gravitational lens galaxies based on the surface brightness distribution of extended arcs and Einstein ring has been introduced by Koopmans 2005 and \citet{V09}. Interestingly, the fraction of substructure measured with this \emph{gravitational imaging technique} is currently in agreement with theoretical expectations (Vegetti et al. 2014).}

\simona{While} future large-scale surveys, such as the LSST, \simona{are expected to deliver new large samples of gravitationally lensed quasar, in the near future the discovery of new systems using} narrow-line quasar emission \citep{N14} \simona{will provide new invaluable statistical perspective on current constraints based on flux ratio anomalies. 
In this paper, we explore the alternative idea that flux ratio anomalies are not related to the presence of substructure but originate in a more complex host galaxy mass distribution than initially considered. To this end we use new infra-red data from the Strong lensing at High Angular Resolution Program(SHARP). The main goal of the SHARP} project \simona{is to re-observe} known quadruple and Einstein ring lens systems at a much higher angular resolution by making use of the Keck adaptive optics (AO) telescope and large interferometric arrays \citep{SHARP12} (Vegetti et al. 2012). \simona{In particular,} to better understand the cause of flux ratio anomalies in strong lens systems \simona{we focus on the lens modelling of the lens system B1555+375 (included in both the observational and theoretical analysis of  \citet{Dalal2002} and \citet{Xu14}, respectively) by making use of} the new information obtained from the latest SHARP infrared imaging. \simona{The paper is organized as follows: the latest SHARP data is introduced in section 2; in section 3 we present the lens model while the results of this analysis and their implication are discussed in section 4.}
%However, only small number of flux ratio anomalous systems in \simona{the} radio are \simona{currently} avaliable. Besides waiting for future large-scale survey such as LSST to find thousands of more new lens galaxies, another approach \simona{is to} seek out more flux ratio anomalous systems \simona{using} narrow-line quasar emission \citep{N14}. 
%	With expected growth in the number of samples, several groups have developed the technique to estimate the properties of substructures from flux ratio anomalous systems. \citet{V09, H13} both analyze the strong lens imaging to detect substructures lie infront of Einstein ring. Their methods improve the detectable mass limit and also show that high spatial resolution imaging is essential for the substructure study. On the other hand, numerical simulations on structure formation do not reach the concise conclusion on flux ratio anomalous systems. The latest study on the cause of flux anomalies from \citet{Xu14} shows the low probability of the existence of substructures in their studied systems. 
%	The Strong lensing at High Angular Resolution Program(SHARP) is a project aims on known quadruple and Einstein ring lensing systems \citep{SHARP12}. We obtain high-resoltion images from Keck adaptive optics(AO) and Hubble Space Telescope(HST) observations. 
%To better understand the cause of flux ratio anomaly in strong lensing systems, we model B1555+375, one of the systems discussed in \citet{Xu14}, with the new information obtained from the latest SHARP infrared imaging. We present the latest SHARP data in part 2, lens model of B1555+375 in part 3, and discussion in part 4.

@@

%\begin{figure}
%\plotone{B1555_Kp.eps}
%\plottwo{B1555_model.eps}{B1555_residue.eps}
%\caption{Left: SHARP K-band image of B1555+375 Middle: Lens model image generated by glafic Right: Residue image of B1555+375.\\
%An edge-on disk can be seen in the center of SHARP K-band image. Exponential disk is marked by the green ellipse in residue image. We believe strong dust extinction from the edge-on disk makes B and D no detection in infrared. Thus leaving two negative holes in our residue.\label{fig1}}
%\end{figure}
%
%\begin{figure}
%\plotone{point_source.eps}
%\caption{Radio observation(red open circle) and model-predicted(blue plus sign) image positions of B1555+375. The position of the source is at $(-0.2066,-0.1634)$ for SIE+Expdisk model, marked by a black filled circle. From left to right, four components are A, B (merging doubles), D(lowest spot), and C(right).\label{fig2}}
%\end{figure}

@@

\section{Discussion}
The abundance of substructure within galaxy-size halo has been an undetermined problem in structure formation studies. The discrepency between numerical simulations and observations within \simona{the} \simona{L}ocal \simona{U}niverse gives two possible arguments: an alternative structure formation model or the selection bias of local universe samples. Lensing shows a promising potential on substructure detection beyond the Local Group. The main reason is that \simona{the} gravitational perturbation from the substructure reflects the total mass, regardless it's luminous or not.
